### 2019-03-27 5_evaluation.tex
read evaluation

In theory, any system should be able to hit peak efficiency as long as
the kernels are well-written and of sufficiently large granularity. In
practice, achieving peak performance is tricky, subject to a number of
pitfalls, and unfortunately, frequently skipped in evaluations of
runtime system overhead. However, verifying that peak performance is
achieved is important to ensuring that such evaluations of overhead and
efficiency are well-grounded and avoid common pitfalls in
configuration.

Figure~\ref{fig:flops} shows the FLOPS achieved with a compute-bound
kernel with varying problem sizes. This is the full version of
Figure~\ref{fig:flops-mpi}. In the best case, we measure peak FLOPS of
$1.26 \times 10^{12}$, which compares favorably with the officially
reported number of $1.2 \times 10^{12}$ \cite{Cori}. For the purposes
of measuring efficiency we use our empirically determined number as
the baseline for 100\% efficiency.

@@

To answer this question, we use the METG metric to determine the
smallest task granularity which can be executed at a given level of
efficiency, as a proxy for overhead. Figure~\ref{fig:metg-compute}
shows how METG(50\%) varies with node count for a variety of
dependence patterns supported by Task Bench:

@@

Most systems for high-performance computing are horizontally scalable,
but this is not true of all the systems included in this
evaluation. Lower is better in Figure~\ref{fig:metg-compute}, and a
flat line is ideal. Lines that rise with node count indicate less than
ideal scaling. Most notably, Spark is typically
intended for use in industrial data center applications with task
granularities measured in tens of seconds. Spark uses a centralized
controller, which limits throughput, and this is visible in the figure
as line for Spark immediately rises with node count. Keep in mind also
that Spark is being evaluated here with a non-trivial dependence
pattern which is relatively unrepresentative of Spark's normal use
cases. Spark is more efficient with trivial parallelism, as described
in Section~\ref{subsec:number-of-dependencies}.

% FIXME: talk about starpu and parsec?

@@

The difference between the remaining systems is due primarily to the
scheduling behavior of the various systems. For example, OpenMP
executes tasks via a thread pool, resulting in a form of work
stealing. This on-node work stealing, in combination with the task
parallelism due to the presence of 4 task graphs, is sufficient to
completely mitigate load imbalance. Systems that exploit task
parallelism but not work stealing on a node achieve lower peak
efficiency, but may achieve smaller task granularities as a result of
not relying on a shared global queue for tasks.

@@

>>>>

In theory, any system should be able to hit peak efficiency as long as
the kernels are well-written and of sufficiently large granularity. In
practice, achieving peak performance is tricky, subject to a number of
pitfalls, and unfortunately, frequently skipped in evaluations of
runtime system overhead. However, verifying that peak performance is
achieved is important to ensure that such evaluations of overhead and
efficiency are well-grounded and avoid common pitfalls in
configuration.

Figure~\ref{fig:flops} shows the FLOPS achieved with a compute-bound
kernel with varying problem sizes. This is the full version of
Figure~\ref{fig:flops-mpi}. In the best case, we measure peak FLOPS of
$1.26 \times 10^{12}$, which compares favorably with the officially
reported number of $1.2 \times 10^{12}$ \cite{Cori}. For the purposes
of measuring efficiency, we use our empirically determined number as
the baseline for 100\% efficiency.

@@

To answer this question, we use the METG metric to determine the
smallest task granularity which can be executed at a given level of
efficiency, as a proxy for overhead. Figure~\ref{fig:metg-compute}
shows how METG(50\%) varies with node count for a variety of
dependence patterns supported by Task Bench. The experiment is conducted
in a weak scale fashion, in which we keep the number of tasks per node
constant while increasing the number of nodes. The detailed explanations
of each dependence pattern are as follows:

@@

Most systems for high-performance computing are horizontally scalable,
but this is not true of all the systems included in this
evaluation. Lower is better in Figure~\ref{fig:metg-compute}, and a
flat line is ideal. Lines that rise with node count indicate less than
ideal scaling. Most notably, Spark is typically
intended for use in industrial data center applications with task
granularities measured in tens of seconds. Spark uses a centralized
controller, which limits throughput, and this is visible in the figure
as line for Spark immediately rises with node count. Keep in mind also
that Spark is being evaluated here with a non-trivial dependence
pattern which is relatively unrepresentative of Spark's normal use
cases. Spark is more efficient with trivial parallelism, as described
in Section~\ref{subsec:number-of-dependencies}. Systems like PaRSEC
and StarPU build the DAG on the fly, so they require to examine all tasks
of the entire DAG on each process. Even though DAG trimming is 
implemented on both systems to not launching tasks on a specific node
if data is not local, the overhead of sweeping all the tasks to 
check data localities goes up with the increasement of
node counts in the weak scale experiment, resulting in poor scalability. 
Even though the PTG implementation relieves the overhead of DAG expansion
from runtime to compile stage, the overhead of determining local tasks
based on data locality leads to un-horizontally scalable. 
The ``PaRSEC DTD Shard'' is an modified implementation of ``PaRSEC DTD''
by pre-partitioning the DAG when assuming data distribution is fixed 
(1D block is used in Task Bench). It removes the cost of sweeping the
entire DAG, and is therefore horizontally scalable.

% FIXME: remove parsec dtd shard if no space.

@@

The difference between the remaining systems is due primarily to the
scheduling behavior of the various systems. For example, OpenMP
execute tasks via a thread pool, resulting in a form of work
stealing. This on-node work stealing, in combination with the task
parallelism due to the presence of 4 task graphs, is sufficient to
completely mitigate load imbalance. Systems that exploit task
parallelism but not work stealing on a node achieve lower peak
efficiency, but may achieve smaller task granularities as a result of
not relying on a shared global queue for tasks.

% FIXME: I am not sure if OpenMP has only 1 thread pool or multiple pools. 
% Systems like StarPU and PaRSEC have multiple pools, but still allows on-node
% work stealing. So I also think the last sentence " may achieve smaller 
% task granularities as a result of not relying on a 
% shared global queue for tasks." is not accurate.

@@

% FIXME why MPI can be affected by other jobs but asynchronous systems can not?
